Declarative Methods Term Project: \\ JumanG

### 2013-05-04 doc/paper.tex
paper.tex. Added more figures

\documentclass{article}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\usepackage{tikz}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

\begin{figure}
\caption{A Sparse Graph with the Springs Solver with Radial Initialization}
\begin{tikzpicture}[scale=0.40, transform shape]
	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
	\node (H4) at (0.16, -4.08) {H4};
	\node (H5) at (-5.44, -2.10) {H5};
	\node (H2) at (3.43, 8.65) {H2};
	\node (H3) at (-4.62, 3.79) {H3};
	\node (H0) at (8.17, 0.76) {H0};
	\node (H1) at (9.03, 6.64) {H1};
	\node (C1) at (-1.14, 0.52) {C1};
	\node (C0) at (4.71, 4.05) {C0};
	\draw [-] (H4)--(C1);
	\draw [-] (H5)--(C1);
	\draw [-] (H2)--(C0);
	\draw [-] (H3)--(C1);
	\draw [-] (H0)--(C0);
	\draw [-] (H1)--(C0);
	\draw [-] (C1)--(C0);
	\draw [-] (C1)--(H3);
	\draw [-] (C1)--(H4);
	\draw [-] (C1)--(H5);
	\draw [-] (C0)--(H0);
	\draw [-] (C0)--(H1);
	\draw [-] (C0)--(H2);
	\draw [-] (C0)--(C1);
\end{tikzpicture}
\end{figure}

\begin{figure}
\caption{A Dense Graph with the Springs Solver with Random Jitter Initialization}
\begin{tikzpicture}[scale=0.50, transform shape]
	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
	\node (k3) at (0.72, 3.87) {k3};
	\node (k2) at (-3.06, -2.52) {k2};
	\node (k1) at (1.41, -3.52) {k1};
	\node (k5) at (-3.49, 2.05) {k5};
	\node (k4) at (3.75, 0.43) {k4};
	\draw [-] (k3)--(k1);
	\draw [-] (k3)--(k2);
	\draw [-] (k3)--(k4);
	\draw [-] (k3)--(k5);
	\draw [-] (k2)--(k1);
	\draw [-] (k2)--(k3);
	\draw [-] (k2)--(k4);
	\draw [-] (k2)--(k5);
	\draw [-] (k1)--(k2);
	\draw [-] (k1)--(k3);
	\draw [-] (k1)--(k4);
	\draw [-] (k1)--(k5);
	\draw [-] (k5)--(k1);
	\draw [-] (k5)--(k2);
	\draw [-] (k5)--(k3);
	\draw [-] (k5)--(k4);
	\draw [-] (k4)--(k1);
	\draw [-] (k4)--(k2);
	\draw [-] (k4)--(k3);
	\draw [-] (k4)--(k5);
\end{tikzpicture}
\end{figure}

@@

%TODO put in an example picture

@@

>>>>

\documentclass{article}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\usepackage{tikz}

\usepackage[english]{babel}
\usepackage{graphicx}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

\begin{figure}
\caption{A Sparsely Connected Graph with the Springs Solver with Radial Initialization}
\begin{tikzpicture}[scale=0.40, transform shape]
	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
	\node (H4) at (0.16, -4.08) {H4};
	\node (H5) at (-5.44, -2.10) {H5};
	\node (H2) at (3.43, 8.65) {H2};
	\node (H3) at (-4.62, 3.79) {H3};
	\node (H0) at (8.17, 0.76) {H0};
	\node (H1) at (9.03, 6.64) {H1};
	\node (C1) at (-1.14, 0.52) {C1};
	\node (C0) at (4.71, 4.05) {C0};
	\draw [-] (H4)--(C1);
	\draw [-] (H5)--(C1);
	\draw [-] (H2)--(C0);
	\draw [-] (H3)--(C1);
	\draw [-] (H0)--(C0);
	\draw [-] (H1)--(C0);
	\draw [-] (C1)--(C0);
	\draw [-] (C1)--(H3);
	\draw [-] (C1)--(H4);
	\draw [-] (C1)--(H5);
	\draw [-] (C0)--(H0);
	\draw [-] (C0)--(H1);
	\draw [-] (C0)--(H2);
	\draw [-] (C0)--(C1);
\end{tikzpicture}
\end{figure}

\begin{figure}
\caption{A Densely Connected Graph with the Springs Solver with Random Jitter Initialization}
\begin{tikzpicture}[scale=0.50, transform shape]
	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
	\node (k3) at (0.72, 3.87) {k3};
	\node (k2) at (-3.06, -2.52) {k2};
	\node (k1) at (1.41, -3.52) {k1};
	\node (k5) at (-3.49, 2.05) {k5};
	\node (k4) at (3.75, 0.43) {k4};
	\draw [-] (k3)--(k1);
	\draw [-] (k3)--(k2);
	\draw [-] (k3)--(k4);
	\draw [-] (k3)--(k5);
	\draw [-] (k2)--(k1);
	\draw [-] (k2)--(k3);
	\draw [-] (k2)--(k4);
	\draw [-] (k2)--(k5);
	\draw [-] (k1)--(k2);
	\draw [-] (k1)--(k3);
	\draw [-] (k1)--(k4);
	\draw [-] (k1)--(k5);
	\draw [-] (k5)--(k1);
	\draw [-] (k5)--(k2);
	\draw [-] (k5)--(k3);
	\draw [-] (k5)--(k4);
	\draw [-] (k4)--(k1);
	\draw [-] (k4)--(k2);
	\draw [-] (k4)--(k3);
	\draw [-] (k4)--(k5);
\end{tikzpicture}
\end{figure}

@@

%TODO put in an example picture
\begin{figure}[h!]
\caption{A Ring Graph solved by the Circo Solver}
\centering
\includegraphics[width=0.3\textwidth]{circo.jpg}
\end{figure}

@@

\begin{figure}
\caption{The same Undirected Ring Graph solved by the Springs Solver}
\begin{tikzpicture}[scale=0.40, transform shape]
	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
	\node (n0) at (-0.17, -0.79) {n0};
	\node (n1) at (-0.17, 4.10) {n1};
	\node (n2) at (4.06, 6.54) {n2};
	\node (n3) at (8.30, 4.09) {n3};
	\node (n4) at (8.30, -0.80) {n4};
	\node (n5) at (4.06, -3.24) {n5};
	\draw [-] (n0)--(n1);
	\draw [-] (n0)--(n5);
	\draw [-] (n1)--(n0);
	\draw [-] (n1)--(n2);
	\draw [-] (n2)--(n1);
	\draw [-] (n2)--(n3);
	\draw [-] (n3)--(n2);
	\draw [-] (n3)--(n4);
	\draw [-] (n4)--(n3);
	\draw [-] (n4)--(n5);
	\draw [-] (n5)--(n4);
	\draw [-] (n5)--(n0);
\end{tikzpicture}
\end{figure}
